\textsf{Are large language models superhuman chemists?}

### 2024-03-20 src/tex/authors.tex
update authors hopefully the last time
one more author
update manuscript

% Question answerers
\credit{Mehrdad Asgari}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Juliane Eberhardt}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Amir Elahi}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Christina Glaubitz}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Maximilian Greiner}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Lea Klepsch}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Yannik Köster}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Fabian Alexander Kreth}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Jakob~Meyer}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Jan Peschel}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Michael Ringleb}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Johanna Schreiber}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Ulrich~S.~Schubert}{0,0,0,1,0,0,0,0,0,0,0,0,0,0}
\credit{Dinga Wonanke}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}

@@

\author[1,$\star$]{Adrian~Mirza~\orcidlink{0000-0003-4033-4235}}
\author[1,$\star$]{Nawaf~Alampara~\orcidlink{}}
\author[1,$\star$]{Sreekanth~Kunchapu~\orcidlink{0009-0003-5752-0154}}
\author[]{Benedict~Emoekabu}
\author[qpi]{Aswanth~Krishnan~\orcidlink{0009-0008-2703-5613}}
\author[nccrcat,liac]{Tanya~Gupta}
\author[1]{Mara~Willhelmi}
\author[1]{Macjonathan~Oreke}

\author[cambridge]{Mehrdad~Asgari~\orcidlink{0000-0002-5427-1610}}
\author[1]{Juliane~Eberhardt~\orcidlink{0009-0000-3991-0704}}
\author[lsmo]{Amir~Elahi}
\author[]{Christina~Glaubitz~\orcidlink{0000-0003-3412-0548}}
\author[1]{Maximilian~Greiner}
\author[1]{Lea~Klepsch~\orcidlink{0000-0003-4978-4670}}
\author[1]{Yannik~Köster~\orcidlink{0000-0002-9125-3067}}
\author[ituc, 2]{Fabian~Alexander~Kreth~\orcidlink{0000-0002-5968-8706}}
\author[1]{Jakob~Meyer}
\author[1]{Jan~Peschel~\orcidlink{0009-0002-4787-2757}}
\author[1]{Michael~Ringleb~\orcidlink{0000-0002-7320-8529}}

\author[1]{Johanna Schreiber}
\author[1]{Ulrich~S.~Schubert~\orcidlink{0000-0003-4978-4670}}
\author[dresden]{Dinga~Wonanke~\orcidlink{0000-0002-9066-2715}}

% Senior authors
\author[open,stability]{Michael Pieler~\orcidlink{0000-0001-9186-7045}}
\author[nccrcat,liac]{Philippe~Schwaller~\orcidlink{0000-0003-3046-6576}}
\author[1,2, 3]{Kevin~Maik~Jablonka~\orcidlink{0000-0003-4894-4660}}

\affil[1]{Laboratory of Organic and Macromolecular Chemistry (IOMC), Friedrich Schiller University Jena, Humboldtstrasse 10, 07743 Jena, Germany}
\affil[2]{Center for Energy and Environmental Chemistry Jena (CEEC Jena), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[3]{Helmholtz Institute for Polymers in Energy Applications (HIPOLE), Philosophenweg 7a, 07743 Jena, Germany}

\affil[liac]{Laboratory of Artificial Chemical Intelligence (LIAC), Institut des Sciences et Ing\'{e}nierie Chimiques, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Lausanne, Switzerland.}
\affil[nccrcat]{National Centre of Competence in Research (NCCR) Catalysis, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Lausanne, Switzerland.}

\affil[lsmo]{Laboratory of Molecular Simulation (LSMO), Institut des Sciences et Ing\'{e}nierie Chimiques, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Sion, Valais, Switzerland.}
\affil[dresden]{Theoretical Chemistry, Technische Universität Dresden, Dresden 01062, Germany}
\affil[open]{OpenBioML.org}
\affil[stability]{Stability.AI}
\affil[ituc]{Institute for Technical Chemistry and Environmental Chemistry (ITUC), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[qpi]{QpiVolta Technologies Pvt Ltd}
\affil[cambridge]{Department of Chemical Engineering \& Biotechnology, University of Cambridge, Philippa Fawcett Drive, Cambridge CB3 0AS, UK}

\affil[]{\texttt{mail@kjablonka.com}}
\affil[$\star$]{These authors contributed equally.}

>>>>

% Question answerers
\credit{Mehrdad Asgari}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Juliane Eberhardt}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Amir Elahi}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Christina Glaubitz}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Maximilian Greiner}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Tim Hoffmann}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Lea Klepsch}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Yannik Köster}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Fabian Alexander Kreth}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Jakob~Meyer}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Jan Peschel}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Michael Ringleb}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Nicole Roesner}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Johanna Schreiber}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}
\credit{Ulrich~S.~Schubert}{0,0,0,1,0,0,0,0,0,0,0,0,0,0}
\credit{Dinga Wonanke}{0,1,0,0,0,0,0,0,0,0,0,0,0,0}

@@

\author[1,$\star$]{Adrian~Mirza~\orcidlink{0000-0003-4033-4235}}
\author[1,$\star$]{Nawaf~Alampara~\orcidlink{}}
\author[1,$\star$]{Sreekanth~Kunchapu~\orcidlink{0009-0003-5752-0154}}
\author[]{Benedict~Emoekabu}
\author[4]{Aswanth~Krishnan~\orcidlink{0009-0008-2703-5613}}
\author[5,6]{Tanya~Gupta}
\author[1]{Mara~Willhelmi}
\author[1]{Macjonathan~Oreke}

\author[7]{Mehrdad~Asgari~\orcidlink{0000-0002-5427-1610}}
\author[1]{Juliane~Eberhardt~\orcidlink{0009-0000-3991-0704}}
\author[8]{Amir~Elahi}
\author[]{Christina~Glaubitz~\orcidlink{0000-0003-3412-0548}}
\author[1]{Maximilian~Greiner}
\author[1]{Tim~Hoffmann}
\author[1]{Lea~Klepsch~\orcidlink{0000-0003-4978-4670}}
\author[1]{Yannik~Köster~\orcidlink{0000-0002-9125-3067}}
\author[2, 9]{Fabian~Alexander~Kreth~\orcidlink{0000-0002-5968-8706}}
\author[1]{Jakob~Meyer}
\author[1]{Jan~Peschel~\orcidlink{0009-0002-4787-2757}}
\author[1]{Michael~Ringleb~\orcidlink{0000-0002-7320-8529}}
\author[1]{Nicole~Roesner}

\author[1]{Johanna Schreiber}
\author[1]{Ulrich~S.~Schubert~\orcidlink{0000-0003-4978-4670}}
\author[10]{Dinga~Wonanke~\orcidlink{0000-0002-9066-2715}}

% Senior authors
\author[11,12]{Michael Pieler~\orcidlink{0000-0001-9186-7045}}
\author[5,6]{Philippe~Schwaller~\orcidlink{0000-0003-3046-6576}}
\author[1,2, 3, \Letter]{Kevin~Maik~Jablonka~\orcidlink{0000-0003-4894-4660}}

\affil[1]{Laboratory of Organic and Macromolecular Chemistry (IOMC), Friedrich Schiller University Jena, Humboldtstrasse 10, 07743 Jena, Germany}
\affil[2]{Center for Energy and Environmental Chemistry Jena (CEEC Jena), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[3]{Helmholtz Institute for Polymers in Energy Applications Jena (HIPOLE Jena), Philosophenweg 7a, 07743 Jena, Germany}

\affil[5]{Laboratory of Artificial Chemical Intelligence (LIAC), Institut des Sciences et Ing\'{e}nierie Chimiques, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Lausanne, Switzerland}
\affil[6]{National Centre of Competence in Research (NCCR) Catalysis, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Lausanne, Switzerland}

\affil[8]{Laboratory of Molecular Simulation (LSMO), Institut des Sciences et Ing\'{e}nierie Chimiques, Ecole Polytechnique F\'{e}d\'{e}rale de Lausanne (EPFL), Sion, Switzerland}
\affil[10]{Theoretical Chemistry, Technische Universität Dresden, Dresden 01062, Germany}
\affil[11]{OpenBioML.org}
\affil[12]{Stability.AI}
\affil[9]{Institute for Technical Chemistry and Environmental Chemistry (ITUC), Friedrich Schiller University Jena, Philosophenweg 7a, 07743 Jena, Germany}
\affil[4]{QpiVolta Technologies Pvt Ltd}
\affil[7]{Department of Chemical Engineering \& Biotechnology, University of Cambridge, Philippa Fawcett Drive, Cambridge CB3 0AS, United Kingdom}

\affil[\Letter]{\texttt{mail@kjablonka.com}}
\affil[$\star$]{These authors contributed equally.}

### 2024-03-20 src/tex/ms.tex
we need to create the heatmap on subsets
update manuscript

\title{\textsf{Are frontier models superhuman chemists?}}

@@

\begin{abstract}
    Large language models (LLMs) have found widespread interest as they can perform tasks they have not been explicitly been trained on. 
    This is relevant for the chemical sciences, which face the problem of learning from many small and diverse datasets that are frequently in the form of text.
    LLMs are increasingly being harnessed to predict chemical properties, optimize reactions, and even design and conduct experiments autonomously.

@@

\begin{figure}
    \centering
    \includegraphics{figures/human_subset_performance.pdf}
    \caption{\textbf{Performance of models and humans on chembench.} The figure shows the percentage of questions that the models answered completely correctly. We use horizontal bars to indicate the performance of various models and highlight statistics of the human performance. 
    Since the humans did not answer all the questions, this plot is based on the subset of questions that most humans answered.
    The metric we use here is harsh as it only considers a question answered completely correctly or completely incorrectly, partially correct answers are also considered as incorrect.
    \Cref{fig:barplot_all_correct_all_questions} gives an overview of the performance of various models on the entire corpus.
    }
    \label{fig:human_vs_models_bar}
    \script{plot_overview_performance_plot.py}
\end{figure}

@@

@@

\section*{Acknowledgements}
This work was supported by the Carl Zeiss Foundation and a \enquote{Talent Fund} of the \enquote{Life} profile line of the Friedrich Schiller University Jena.
We also want to acknowledge access to the HPC cluster of Stability.AI.
M.A. expresses gratitude to the European Research Council (ERC) for evaluating the project with the reference number 101106377 titled ‘‘CLARIFIER’’ and accepting it for funding under the HORIZON TMA MSCA Postdoctoral Fellowships - European Fellowships. 
Furthermore, M.A. acknowledges the funding provided by UK Research and Innovation (UKRI) under the UK government’s Horizon Europe funding guarantee (Grant Reference: EP/Y023447/1; Organization Reference: 101106377).

@@

\section*{Conflicts of interest}
K.M.J.\ is a paid consultant for OpenAI. M.P.\ is employee of Stability.ai and A.M.\ and N.A.\ are paid contractors of Stability.AI.

@@

\clearpage
\begin{refsection}
\appendix
\section{Appendix}
\input{appendix.tex}

\printbibliography[heading=subbibintoc]
\end{refsection}
\end{document}

>>>>

\title{\textsf{Are large language models superhuman chemists?}}

@@

\clearpage
\begin{abstract}
    Large language models (LLMs) have found widespread interest as they can perform tasks they have not been explicitly been trained on. 
    This is relevant for the chemical sciences, which face the problem of learning from many small and diverse datasets that are frequently in the form of text.
    LLMs are increasingly being harnessed to predict chemical properties, optimize reactions, and even design and conduct experiments autonomously.

@@

\begin{figure}
    \centering
    \includegraphics{figures/human_subset_performance.pdf}
    \caption{\textbf{Performance of models and humans on \chembench.} The figure shows the percentage of questions that the models answered completely correctly. We use horizontal bars to indicate the performance of various models and highlight statistics of the human performance. 
    Since the humans did not answer all the questions, this plot is based on the subset of questions that most humans answered.
    The metric we use here is harsh as it only considers a question answered completely correctly or completely incorrectly, partially correct answers are also considered as incorrect.
    \Cref{fig:barplot_all_correct_all_questions} gives an overview of the performance of various models on the entire corpus.
    }
    \label{fig:human_vs_models_bar}
    \script{plot_overview_performance_plot.py}
\end{figure}

@@

%%%%% IMPORTANT emphasize the importance of breadth as performance on tasks does not necessarily correlate with performance on other tasks

@@

\section*{Acknowledgements}
This work was supported by the Carl Zeiss Foundation and a \enquote{Talent Fund} of the \enquote{Life} profile line of the Friedrich Schiller University Jena.
We also want to acknowledge access to the HPC cluster of Stability.AI.
M.A. expresses gratitude to the European Research Council (ERC) for evaluating the project with the reference number 101106377 titled \enquote{CLARIFIER} and accepting it for funding under the HORIZON TMA MSCA Postdoctoral Fellowships - European Fellowships. 
Furthermore, M.A. acknowledges the funding provided by UK Research and Innovation (UKRI) under the UK government’s Horizon Europe funding guarantee (Grant Reference: EP/Y023447/1; Organization Reference: 101106377).

@@

\section*{Conflicts of interest}
K.M.J.\ is a paid consultant for OpenAI (as part of the red teaming network). M.P.\ is employee of Stability.ai and A.M.\ and N.A.\ are paid contractors of Stability.AI.

@@

\clearpage
\begin{refsection}
\appendix
\section{Appendix}
\input{appendix.tex}
\clearpage
\printbibliography[heading=subbibintoc]
\end{refsection}
\end{document}
